---
output: github_document
---

*This repository is an activity completed by [Zehui Yin](https://zehuiyin.github.io/) for the course [GEOG 712 Reproducible Research Workflow with GitHub and R](https://academiccalendars.romcmaster.ca/preview_course.php?catoid=55&coid=274877), taught by [Dr. Antonio Paez](https://experts.mcmaster.ca/display/paezha) in Fall 2024.*

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# reproducible-paper-repo

<!-- badges: start -->
<!-- badges: end -->

## About this repo

This is a template repository with a folder structure that works well for reproducible papers.

This readme file when knitted will become the landing page of the GitHub repository.

It can contain chunks of code because the source document is Rmd.

For example:
```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub.

The folder structure and the contents of the folders are suggestions and/or examples. Keep or delete as you wish.